---
title: "Small Area Estimation - UFH, MFH & Comparison Report"
author: "EU SAE Pipeline"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
params:
  include_ai: false
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: cosmo
    self_contained: true
    fig_width: 10
    fig_height: 6
    md_extensions: "-smart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)

suppressPackageStartupMessages({
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(readxl)
  library(knitr)
  library(patchwork)
  library(sf)
  library(scales)
  library(here)
})

# Keep report inputs and outputs inside the running package copy when the
# package is nested within a different Git checkout.
here::i_am("report.Rmd")

fig_dir   <- here::here("outputs", "figures")
data_dir  <- here::here("outputs", "data")
table_dir <- here::here("outputs", "tables")

`%||%` <- function(x, y) {
  if (is.null(x) || length(x) == 0) y else x
}

source(here::here("R", "comparison_report_ai.R"), local = knitr::knit_global())

include_fig <- function(filename, ...) {
  path <- file.path(fig_dir, filename)
  if (file.exists(path)) {
    knitr::include_graphics(path)
  } else {
    cat(sprintf("*Figure not available: %s*\n", filename))
  }
}

safe_read_csv <- function(filename, dir = table_dir) {
  path <- file.path(dir, filename)
  if (file.exists(path)) read.csv(path) else NULL
}
```

# Executive Summary

```{r load-comparison}
pov_fh  <- tryCatch(read_excel(file.path(data_dir, "pov_fh.xlsx")),
                     error = function(e) NULL)
pov_mfh <- tryCatch(read_excel(file.path(data_dir, "pov_mfh.xlsx")),
                     error = function(e) NULL)
pov_cmp <- tryCatch(read_excel(file.path(data_dir, "pov_comparison_detailed.xlsx")),
                     error = function(e) NULL)
mfh_artifacts <- tryCatch(readRDS(file.path(data_dir, "mfh_artifacts.rds")),
                          error = function(e) NULL)
run_meta <- tryCatch(readRDS(file.path(data_dir, "run_metadata.rds")),
                     error = function(e) NULL)
ai_state <- tryCatch(readRDS(file.path(data_dir, "ai_interpretations.rds")),
                     error = function(e) NULL)

sig_summary <- safe_read_csv("significance_summary.csv",
                              file.path(fig_dir, "tables"))
exec_summary <- safe_read_csv("executive_summary.csv",
                               file.path(fig_dir, "tables"))

model_fit_diag <- safe_read_csv("model_fit_diagnostics.csv",
                                file.path(fig_dir, "tables"))
if (is.null(model_fit_diag)) {
  fit_parts <- list(
    safe_read_csv("ufh_model_diagnostics.csv"),
    safe_read_csv("mfh_model_diagnostics.csv")
  )
  fit_parts <- fit_parts[!vapply(fit_parts, is.null, logical(1))]
  model_fit_diag <- if (length(fit_parts) > 0) bind_rows(fit_parts) else NULL
}

selection_parts <- list(
  safe_read_csv("ufh_selection_diagnostics.csv"),
  safe_read_csv("mfh_selection_diagnostics.csv")
)
selection_parts <- selection_parts[!vapply(selection_parts, is.null, logical(1))]
selection_diag <- if (length(selection_parts) > 0) bind_rows(selection_parts) else NULL
mfh_numerical_diag <- safe_read_csv("mfh_numerical_diagnostics.csv")
mfh_variance_selection <- safe_read_csv("mfh_variance_structure_selection.csv")
mfh_mcpe_validation <- safe_read_csv("mfh_mcpe_validation.csv")
```

```{r ai-report-styles, results='asis'}
cat(comparison_ai_styles_html())
cat(paste0(
  '<style>',
  '.full-significance-table{max-height:760px;overflow:auto;border:1px solid #d9e2ec;',
  'margin:16px 0 22px 0;background:#fff;}',
  '.full-significance-table table{min-width:1180px;margin-bottom:0;font-size:.92em;}',
  '.full-significance-table thead th{position:sticky;top:0;background:#fff;z-index:2;',
  'border-bottom:2px solid #cbd5e1;}',
  '.excel-output-links{background:#f7fafc;border-left:5px solid #486581;',
  'padding:12px 16px;margin:18px 0;}',
  '</style>'
))
```

```{r exec-summary-table}
if (!is.null(exec_summary)) {
  kable(exec_summary, digits = 4,
        caption = "Mean estimates and mean MSEs by year")
}
```

```{r sig-summary-table}
if (!is.null(sig_summary)) {
  kable(sig_summary, digits = 0,
        caption = "Number of domains with statistically significant changes")
}
```

# Run Setup

```{r run-setup}
if (!is.null(run_meta)) {
  bm <- run_meta$benchmarking %||% list()
  ai_meta <- run_meta$ai_interpretations %||% list()
  generated_sections <- ai_meta$generated_sections %||% character()
  generated_sections_label <- if (length(generated_sections)) {
    paste(generated_sections, collapse = ", ")
  } else {
    "none"
  }
  numeric_qa <- ai_meta$numeric_qa_status %||% character()
  numeric_qa_label <- if (length(numeric_qa)) {
    paste(sprintf("%s=%s", names(numeric_qa), numeric_qa), collapse = ", ")
  } else {
    "not performed"
  }
  mfh_variance_rule <- run_meta$mfh_variance_structure_selection %||% list()
  mfh_refvar_label <- if (isTRUE(mfh_variance_rule$test_available)) {
    paste0(mfh_variance_rule$adjustment %||% "not recorded", " (applied)")
  } else {
    paste0(
      "not applied",
      if (nzchar(mfh_variance_rule$reason %||% "")) {
        paste0(" - ", mfh_variance_rule$reason)
      } else {
        ""
      }
    )
  }
  setup_tbl <- data.frame(
    Item = c(
      "Application version",
      "Country or territory",
      "Run ID",
      "Run label",
      "Run folder",
      "Archived outputs",
      "Benchmarking",
      "Benchmark level",
      "Benchmark source",
      "Benchmark target file",
      "Requested MFH rule",
      "Selected MFH model",
      "MFH3 reference-variance test adjustment",
      "Analysis seed",
      "MCPE bootstrap replicates",
      "UFH change variance assumption",
      "Poverty-change inference",
      "External AI enabled",
      "AI interpretations included",
      "AI provider and model",
      "AI sections generated",
      "AI numeric QA (warning-only)",
      "AI human-review status"
    ),
    Value = c(
      run_meta$application_version %||% "",
      run_meta$country_or_territory %||% "Not specified",
      run_meta$run_id %||% "",
      run_meta$run_label %||% "",
      run_meta$run_folder %||% "",
      run_meta$archived_outputs %||% "",
      if (isTRUE(bm$enabled)) "enabled" else "off",
      bm$level_label %||% bm$level %||% "",
      bm$source %||% "",
      bm$target_path %||% "",
      run_meta$mfh_requested_model %||% "",
      run_meta$mfh_selected_model %||% "",
      mfh_refvar_label,
      run_meta$analysis_seed %||% "",
      run_meta$mcpe_bootstrap_replicates %||% "",
      run_meta$ufh_change_variance_assumption %||% "",
      "pointwise primary; BH and Bonferroni sensitivities reported",
      if (isTRUE(run_meta$ai$enabled)) "yes (advisory commentary only)" else "no",
      if (isTRUE(params$include_ai)) "yes, where successfully generated" else "no",
      paste(
        ai_meta$provider %||% run_meta$ai$provider %||% "not recorded",
        ai_meta$model %||% "model not recorded",
        sep = " / "
      ),
      generated_sections_label,
      numeric_qa_label,
      ai_meta$human_review_status %||% "not reviewed"
    ),
    check.names = FALSE
  )
  kable(setup_tbl, caption = "Run configuration and output locations")
}
```

# Comparison of UFH and MFH

This section compares the univariate (UFH) and multivariate (MFH) Fay-Herriot pipelines side by side, examining regression formulas, normality diagnostics, precision metrics, poverty maps, RMSE maps, and change analyses.

```{r ai-overview, results='asis'}
cat(comparison_ai_assurance_html(ai_state, include_ai = isTRUE(params$include_ai)))
cat(comparison_ai_section_html(ai_state, "overview",
                               include_ai = isTRUE(params$include_ai)))
```

```{r mfh-availability, results='asis'}
mfh_status <- if (!is.null(mfh_artifacts)) {
  list(
    fit_failed  = isTRUE(mfh_artifacts$model_fit_failed),
    refvar_zero = isTRUE(mfh_artifacts$refvar_zero),
    var_choice  = mfh_artifacts$var_choice %||% "(unset)",
    cov_choice  = mfh_artifacts$cov_choice %||% "(unset)",
    requested_model = mfh_artifacts$diag_model_requested %||% "(unset)",
    diag_model  = mfh_artifacts$diag_model %||% "(unset)",
    selection_reason = (mfh_artifacts$variance_structure_selection %||% list())$reason %||% "not recorded",
    bad_rows    = mfh_artifacts$bad_vardir_rows %||% 0L,
    n_domains   = mfh_artifacts$n_domains %||% NA_integer_,
    n_fitted    = mfh_artifacts$n_domains_fitted %||% mfh_artifacts$n_domains %||% NA_integer_
  )
} else {
  NULL
}

mfh_not_executed <- !is.null(mfh_status) &&
  (mfh_status$fit_failed || mfh_status$refvar_zero)

mfh_change <- safe_read_csv("comparison_final.csv")
mfh_change_available <- !is.null(mfh_change) &&
  "diff" %in% names(mfh_change) &&
  any(is.finite(suppressWarnings(as.numeric(mfh_change$diff))))

if (!is.null(mfh_status) && mfh_status$bad_rows > 0 && !mfh_not_executed) {
  cat(sprintf(
    paste0(
      "<div class=\"alert alert-info\">",
      "<strong>Note:</strong> %s of %s domains had missing/non-finite sampling variances ",
      "and were excluded from MFH fitting. Their MFH estimates are reported as NA. ",
      "The MFH model was fitted on the remaining %s domains.",
      "</div>\n"
    ),
    mfh_status$bad_rows,
    mfh_status$n_domains,
    mfh_status$n_fitted
  ))
}

if (!is.null(mfh_status) && !mfh_not_executed) {
  cat(sprintf(
    paste0(
      "<div class=\"alert alert-info\">",
      "<strong>Selected MFH variant:</strong> %s (requested rule: %s). ",
      "Selection reason: %s ",
      "The displayed MFH comparison tables and plots use the selected model export ",
      "from <code>pov_mfh.xlsx</code>. Other MFH variants may be fitted internally ",
      "for diagnostics/model selection, but they are not exposed in the user-facing ",
      "MFH estimate export.",
      "</div>\n"
    ),
    mfh_status$diag_model,
    mfh_status$requested_model,
    mfh_status$selection_reason
  ))
}

if (mfh_not_executed) {
  if (mfh_status$fit_failed) {
    reason <- "The selected MFH model did not return a valid fit object."
  } else {
    reason <- "The selected MFH model estimated the random-effects variance at zero, so no domain-specific shrinkage was produced."
  }

  cat(sprintf(
    paste0(
      "<div class=\"alert alert-warning\">",
      "<strong>MFH was not executed for this configuration.</strong><br>",
      "%s<br>",
      "Selected options: <code>var_choice = %s</code>, <code>cov_choice = %s</code>, ",
      "<code>diagnostic model = %s</code>.<br>",
      "MFH maps, UFH-vs-MFH comparisons, and MFH change analyses are omitted or NA-filled.",
      "</div>\n"
    ),
    reason,
    mfh_status$var_choice,
    mfh_status$cov_choice,
    mfh_status$diag_model
  ))
} else if (!is.null(mfh_status) && !mfh_change_available) {
  cat(
    paste0(
      "<div class=\"alert alert-info\">",
      "<strong>MFH fitted, but MFH change analysis is not available.</strong><br>",
      "The level estimates are available, but the MCPE-based change analysis did not produce finite differences. ",
      "This can happen with raw direct variances in the parametric bootstrap.",
      "</div>\n"
    )
  )
}
```

## MFH Variance-Structure Selection

The default procedure fits MFH3 first. If MFH3 does not converge or cannot be fitted, the reason is recorded and MFH2 is used. If MFH3 converges, its reference-variance tests compare the time-specific random-effect variances. MFH3 is retained when at least one adjusted test rejects equality at the configured level; otherwise MFH2 is selected. Bonferroni is the confirmatory default, while Benjamini-Hochberg (BH) is available as a less-conservative sensitivity option. These adjustments apply across pairwise **time-variance contrasts**, not across geographic areas. With two analysis years there is only one contrast, so raw, Bonferroni, and BH p-values are identical.

```{r mfh-variance-selection-table}
if (!is.null(mfh_variance_selection)) {
  kable(mfh_variance_selection, digits = 4,
        caption = "MFH3 convergence and reference-variance model-selection decision")
}
```

## MCPE Bootstrap Assurance

The table below reports run-specific computational diagnostics for the parametric-bootstrap MCPE calculation, including successful refits, failures, covariance repairs, and Monte Carlo standard errors. These diagnostics assess numerical execution and simulation precision; they do not, by themselves, constitute an independent validation of statistical bias or interval coverage.

```{r mfh-mcpe-validation-table}
if (!is.null(mfh_mcpe_validation)) {
  kable(mfh_mcpe_validation, digits = 5,
        caption = "MCPE bootstrap execution and Monte Carlo precision diagnostics")
}
```

## Regression Models

```{r formula-table}
formulas <- safe_read_csv("model_formulas.csv",
                           file.path(fig_dir, "tables"))
if (!is.null(formulas)) {
  kable(formulas,
        caption = "Selected regression formulas used in the FH and MFH pipelines")
}
```

## Model Fit Diagnostics

The R2 and adjusted R2 values below are OLS companion diagnostics for the selected formulas. They are useful for model screening and communication, but they are not a definitive mixed-model fit measure.

```{r model-fit-diagnostics}
if (!is.null(model_fit_diag) && nrow(model_fit_diag) > 0) {
  fit_display <- model_fit_diag %>%
    transmute(
      Method = method,
      Year = year,
      Formula = formula,
      `Domains used` = n_domains,
      `Predictors` = n_predictors,
      AIC = round(as.numeric(AIC), 4),
      BIC = round(as.numeric(BIC), 4),
      logLik = round(as.numeric(logLik), 4),
      Sigma = round(as.numeric(residual_sd), 4),
      `Random-effect variance` = round(as.numeric(random_effect_variance), 6),
      `OLS companion R2` = round(as.numeric(ols_companion_r2), 4),
      `OLS companion adjusted R2` = round(as.numeric(ols_companion_adj_r2), 4)
    )
  kable(fit_display,
        caption = "Model fit diagnostics for selected UFH and MFH formulas")
} else {
  cat("*Model fit diagnostics were not exported for this run.*\n")
}
```

## MFH Numerical Diagnostics

The table below records the inversion method and condition-number diagnostic
for the robust MFH2 fit. Successful Cholesky paths report a low-cost estimate
derived from the Cholesky factor; fallback paths report an exact value when it
can be computed. A generalized inverse or an unavailable Fisher-information
inverse requires review. When `g3_available` is false, the package reports MSE
and CV as unavailable rather than substituting a partial MSE.

```{r mfh-numerical-diagnostics, results='asis'}
if (!is.null(mfh_numerical_diag) && nrow(mfh_numerical_diag) > 0) {
  print(kable(mfh_numerical_diag,
              digits = 4,
              caption = "MFH numerical diagnostics and g3/MSE availability"))
  needs_attention <- any(
    mfh_numerical_diag$diagnostic_status %in%
      c("generalized_inverse_used", "unavailable", "robust_refit_failed",
        "robust_refit_no_extended_diagnostics", "model_fit_failed",
        "model_fit_skipped") |
      mfh_numerical_diag$mse_status == "unavailable_fisher_information",
    na.rm = TRUE
  )
  if (needs_attention) {
    cat("\n> **Review required:** MFH numerical diagnostics indicate a generalized inverse, an unavailable inverse, a failed/skipped fit, or unavailable g3/MSE.\n")
  }
} else {
  cat("*MFH numerical diagnostics were not exported for this run.*\n")
}
```

## Covariate Selection Diagnostics

This table records whether LASSO screening was used before stepwise selection. When LASSO is off, the stepwise procedure receives the original candidate set.

```{r selection-diagnostics}
if (!is.null(selection_diag) && nrow(selection_diag) > 0) {
  selection_display <- selection_diag %>%
    mutate(
      lasso_enabled = as.character(lasso_enabled),
      lambda_choice = as.character(lambda_choice),
      fallback_used = as.character(fallback_used)
    ) %>%
    transmute(
      Model = model,
      Outcome = outcome,
      `LASSO screening` = ifelse(tolower(lasso_enabled) %in% c("true", "yes", "1"),
                                 "on", "off"),
      `Lambda choice` = lambda_choice,
      `Candidate variables` = n_candidates,
      `Numeric candidates` = n_numeric_candidates,
      `Complete cases for LASSO` = n_complete_cases,
      `LASSO-selected variables` = n_selected,
      `Fallback used` = fallback_used,
      Note = note
    )
  kable(selection_display,
        caption = "Covariate screening diagnostics before stepwise model selection")
} else {
  cat("*Covariate selection diagnostics were not exported for this run.*\n")
}
```

```{r coef-fh}
fh_coefs <- safe_read_csv("fh_coefficients.csv",
                           file.path(fig_dir, "tables"))
if (!is.null(fh_coefs)) {
  kable(fh_coefs, digits = c(0, 0, 0, 6, 6, 3, 4, 0),
        caption = "Estimated FH regression coefficients by year")
}
```

```{r coef-mfh}
mfh_coefs <- safe_read_csv("mfh_coefficients.csv",
                            file.path(fig_dir, "tables"))
if (!is.null(mfh_coefs)) {
  kable(mfh_coefs, digits = c(0, 0, 0, 6, 6, 3, 4, 0),
        caption = "Estimated MFH regression coefficients by year")
}
```

## Normality Diagnostics

```{r normality-tests}
normality <- safe_read_csv("normality_tests.csv",
                            file.path(fig_dir, "tables"))
if (!is.null(normality)) {
  kable(normality, digits = 4,
        caption = "Shapiro-Wilk normality tests for FH and MFH diagnostics")
}
```

### Q-Q Plots

```{r qq-plots, results='asis'}
qq_files <- list.files(file.path(fig_dir, "diagnostics"),
                       pattern = "^qq_.*\\.png$", full.names = FALSE)
if (length(qq_files) > 0) {
  for (f in sort(qq_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("\n#### %s\n\n", label))
    cat(sprintf("![%s](%s)\n\n", label,
                file.path(fig_dir, "diagnostics", f)))
  }
} else {
  cat("*No Q-Q plots available.*\n")
}
```

### Density Plots

```{r density-plots, results='asis'}
density_files <- list.files(file.path(fig_dir, "diagnostics"),
                            pattern = "^density_.*\\.png$", full.names = FALSE)
if (length(density_files) > 0) {
  for (f in sort(density_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("\n#### %s\n\n", label))
    cat(sprintf("![%s](%s)\n\n", label,
                file.path(fig_dir, "diagnostics", f)))
  }
} else {
  cat("*No density plots available.*\n")
}
```

```{r ai-normality, results='asis'}
cat(comparison_ai_section_html(ai_state, "normality",
                               include_ai = isTRUE(params$include_ai)))
```

## Rate, MSE, RMSE, and CV Comparisons

```{r metric-comparisons, results='asis'}
mc_files <- list.files(file.path(fig_dir, "metric_comparisons"),
                       pattern = "\\.png$", full.names = FALSE)
if (length(mc_files) > 0) {
  for (f in sort(mc_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("\n### %s\n\n", label))
    cat(sprintf("![%s](%s)\n\n", label,
                file.path(fig_dir, "metric_comparisons", f)))
  }
} else {
  cat("*No metric comparison plots available.*\n")
}
```

```{r ai-rates-precision, results='asis'}
cat(comparison_ai_section_html(ai_state, "rates",
                               include_ai = isTRUE(params$include_ai)))
cat(comparison_ai_section_html(ai_state, "precision",
                               include_ai = isTRUE(params$include_ai)))
```

## Poverty Maps

```{r poverty-maps, results='asis'}
map_files <- list.files(file.path(fig_dir, "poverty_maps"),
                        pattern = "\\.png$", full.names = FALSE)
if (length(map_files) > 0) {
  for (f in sort(map_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("\n### %s\n\n", label))
    cat(sprintf("![%s](%s)\n\n", label,
                file.path(fig_dir, "poverty_maps", f)))
  }
} else {
  cat("*No poverty maps available.*\n")
}
```

```{r ai-poverty-maps, results='asis'}
cat(comparison_ai_section_html(ai_state, "poverty_maps",
                               include_ai = isTRUE(params$include_ai)))
```

## RMSE Maps

Maps of the root mean squared error (RMSE) of the poverty estimates, showing
how estimation precision varies across domains. Darker areas indicate higher
RMSE (lower precision).

```{r rmse-maps, results='asis'}
rmse_map_files <- list.files(file.path(fig_dir, "rmse_maps"),
                             pattern = "\\.png$", full.names = FALSE)
if (length(rmse_map_files) > 0) {
  for (f in sort(rmse_map_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("\n### %s\n\n", label))
    cat(sprintf("![%s](%s)\n\n", label,
                file.path(fig_dir, "rmse_maps", f)))
  }
} else {
  cat("*No RMSE maps available.*\n")
}
```

## Statistical Significance of Poverty Changes

The primary significance status is pointwise at alpha = 0.05: a domain is
classified as significant when its unadjusted two-sided p-value is below 0.05,
equivalently when the plotted pointwise 95% confidence interval excludes zero.
The table also reports Benjamini-Hochberg (BH) and Bonferroni adjustments across
the geographic domains within each method. BH controls the false discovery rate;
Bonferroni controls the family-wise probability of any false rejection. These
are sensitivity results and do not control the figure colors or headline counts.
They are separate from the MFH3 reference-variance test adjustment, which applies
only to pairwise time-variance contrasts when MFH3 is fitted.

```{r sig-comparison, results='asis'}
sig_cmp <- tryCatch(
  read_excel(file.path(data_dir, "statistical_significance_comparison.xlsx")),
  error = function(e) NULL
)
if (!is.null(sig_cmp)) {
  sig_cols <- c(
    "domain", "method", "diff", "mse", "lb", "ub",
    "p_value", "significant_unadjusted",
    "p_value_bh", "significant_bh",
    "p_value_bonferroni", "significant_bonferroni"
  )
  sig_display <- sig_cmp %>%
    select(any_of(sig_cols)) %>%
    mutate(
      .method_order = match(
        as.character(method),
        c("FH", "FH Benchmarked", "MFH", "MFH Benchmarked")
      ),
      .domain_order = suppressWarnings(as.numeric(as.character(domain)))
    ) %>%
    arrange(.method_order, is.na(.domain_order), .domain_order, domain) %>%
    select(-.method_order, -.domain_order)
  sig_labels <- c(
    domain = "Domain", method = "Method", diff = "Change", mse = "MSE",
    lb = "95% CI lower", ub = "95% CI upper",
    p_value = "Pointwise p-value",
    significant_unadjusted = "Pointwise significant",
    p_value_bh = "BH-adjusted p-value",
    significant_bh = "BH significant",
    p_value_bonferroni = "Bonferroni-adjusted p-value",
    significant_bonferroni = "Bonferroni significant"
  )
  names(sig_display) <- unname(sig_labels[names(sig_display)])
  cat('<div class="full-significance-table">')
  cat(as.character(kable(
    sig_display,
    format = "html",
    digits = 4,
    escape = TRUE,
    table.attr = 'class="table table-condensed"',
    caption = sprintf(
      "Complete statistical significance comparison (%d rows; pointwise status is primary)",
      nrow(sig_display)
    )
  )))
  cat('</div>')
} else {
  cat("*The statistical-significance workbook was not available for this run.*\n")
}
```

### Distribution and paired comparison of estimated changes

These two figures compare the **estimated changes themselves**, using the later
year minus the earlier year. Poverty-rate changes are in **percentage points**;
mean-welfare changes use the configured currency units. Negative values indicate
a decrease. The same finite, matched domain pairs enter both plots. The boxplot
shows the distribution across domains, not the uncertainty around each estimate.
Below the scatterplot's equality line, the MFH estimate is lower than the UFH
estimate; that does not establish greater accuracy or statistical significance.
These comparisons use unbenchmarked estimates, as do the CI-width figures below.

```{r change-estimate-summary, results='asis'}
change_path <- file.path(data_dir, "change_estimate_comparison.xlsx")
change_summary <- tryCatch(read_excel(change_path, sheet = "Distribution summary"), error = function(e) NULL)
change_paired <- tryCatch(read_excel(change_path, sheet = "Paired summary"), error = function(e) NULL)
if (!is.null(change_summary) && nrow(change_summary)) {
  display <- change_summary[, c("method", "domains", "minimum", "median", "mean", "maximum", "unit")]
  names(display) <- c("Method", "Domains", "Minimum", "Median", "Mean", "Maximum", "Unit")
  print(kable(display, digits = 2, caption = "Estimated changes across matched domains (unweighted domain summaries)"))
}
if (!is.null(change_paired) && nrow(change_paired)) {
  p <- change_paired[1, ]
  cat(sprintf("\n\n**%s minus %s:** %d finite matched domains. MFH changes are lower in %d, higher in %d, and equal in %d domains. The median paired difference (MFH minus UFH) is %.2f %s. These are descriptive comparisons, not tests of the difference between estimators.\n\n",
    p$year_to, p$year_from, p$finite_paired_domains, p$MFH_lower_domains,
    p$MFH_higher_domains, p$equal_domains, p$median_MFH_minus_UFH_change, p$unit))
  if (p$excluded_nonfinite_pairs + p$UFH_only_domains + p$MFH_only_domains > 0) {
    cat(sprintf("Excluded: %d matched pairs with nonfinite changes; %d UFH-only and %d MFH-only domains.\n\n",
      p$excluded_nonfinite_pairs, p$UFH_only_domains, p$MFH_only_domains))
  }
}
```

```{r change-estimate-figures}
change_paths <- file.path(fig_dir, "change_comparisons",
  c("change_distribution_ufh_mfh.png", "change_paired_ufh_mfh.png"))
change_paths <- change_paths[file.exists(change_paths)]
if (length(change_paths)) knitr::include_graphics(change_paths) else
  cat("*No finite matched UFH-MFH changes are available for these figures.*\n")
```

### Distribution of 95% confidence-interval widths

The figures below compare the full width of each pointwise 95% confidence
interval (`upper bound - lower bound`) across matched domains. The first figure
shows the two distributions; the second preserves the domain-level pairing.
Points below the dashed equality line have narrower MFH intervals. A narrower
interval does not by itself imply a significant change, because significance
also depends on how far the estimated change lies from zero.

```{r ci-width-summary, results='asis'}
ci_width_path <- file.path(data_dir, "ci_width_comparison.xlsx")
ci_width_domain <- tryCatch(
  read_excel(ci_width_path, sheet = "Domain comparison"),
  error = function(e) NULL
)
ci_width_summary <- tryCatch(
  read_excel(ci_width_path, sheet = "Distribution summary"),
  error = function(e) NULL
)
ci_width_paired <- tryCatch(
  read_excel(ci_width_path, sheet = "Paired summary"),
  error = function(e) NULL
)

if (!is.null(ci_width_summary) && nrow(ci_width_summary) > 0) {
  ci_summary_display <- ci_width_summary
  names(ci_summary_display) <- c(
    method = "Method", domains = "Domains", minimum = "Minimum",
    percentile_25 = "25th percentile", median = "Median", mean = "Mean",
    percentile_75 = "75th percentile", maximum = "Maximum", unit = "Unit"
  )[names(ci_summary_display)]
  cat(as.character(kable(
    ci_summary_display,
    format = "html",
    digits = 2,
    escape = TRUE,
    table.attr = 'class="table table-condensed"',
    caption = "Distribution of pointwise 95% confidence-interval widths"
  )))
}

if (!is.null(ci_width_paired) && nrow(ci_width_paired) > 0) {
  .paired <- ci_width_paired[1, ]
  cat(sprintf(
    paste0(
      "<p><strong>Paired-domain result.</strong> MFH intervals are narrower in ",
      "%d of %d matched domains and wider in %d. The median MFH interval is ",
      "%.1f%% narrower than the corresponding UFH interval; the median paired ",
      "width difference (MFH minus UFH) is %.2f %s.</p>"
    ),
    as.integer(.paired$MFH_narrower_domains),
    as.integer(.paired$matched_domains),
    as.integer(.paired$MFH_wider_domains),
    as.numeric(.paired$median_MFH_percent_width_reduction),
    as.numeric(.paired$median_MFH_minus_UFH_width),
    as.character(.paired$unit)
  ))
}
```

```{r ci-width-figures}
ci_figure_paths <- file.path(
  fig_dir,
  "uncertainty_comparisons",
  c("ci_width_distribution_ufh_mfh.png", "ci_width_paired_ufh_mfh.png")
)
ci_figure_paths <- ci_figure_paths[file.exists(ci_figure_paths)]
if (length(ci_figure_paths) > 0) {
  knitr::include_graphics(ci_figure_paths)
} else {
  cat("*Confidence-interval width figures were not available for this run.*\n")
}
```

```{r excel-result-links, results='asis'}
excel_outputs <- c(
  "Complete consolidated result tables" = "EU_SAE_results.xlsx",
  "Full pointwise, BH, and Bonferroni significance table" = "statistical_significance_comparison.xlsx",
  "Confidence-interval width tables" = "ci_width_comparison.xlsx",
  "Estimated-change comparison tables" = "change_estimate_comparison.xlsx",
  "Detailed UFH-MFH estimate comparison" = "pov_comparison_detailed.xlsx"
)
available_excel <- excel_outputs[file.exists(file.path(data_dir, excel_outputs))]
if (length(available_excel) > 0) {
  cat('<div class="excel-output-links"><strong>Excel result tables</strong><ul>')
  for (label in names(available_excel)) {
    cat(sprintf(
      '<li><a href="data/%s">%s</a></li>',
      html_escape_text(available_excel[[label]]),
      html_escape_text(label)
    ))
  }
  cat('</ul></div>')
}
```

```{r ai-change-significance, results='asis'}
cat(comparison_ai_section_html(ai_state, "change_significance",
                               include_ai = isTRUE(params$include_ai)))
```

```{r change-figures, results='asis'}
change_files <- list.files(file.path(fig_dir, "change_figures"),
                           pattern = "\\.png$", full.names = FALSE)
if (length(change_files) > 0) {
  for (f in sort(change_files)) {
    label <- gsub("_", " ", tools::file_path_sans_ext(f))
    cat(sprintf("\n### %s\n\n", label))
    cat(sprintf("![%s](%s)\n\n", label,
                file.path(fig_dir, "change_figures", f)))
  }
} else {
  cat("*No change figures available.*\n")
}
```

```{r ai-change-maps, results='asis'}
cat(comparison_ai_section_html(ai_state, "change_maps",
                               include_ai = isTRUE(params$include_ai)))
```

# Session Information

```{r session-info}
session_path <- here::here("outputs", "data", "session_info.txt")
if (file.exists(session_path)) {
  cat("```\n")
  cat(readLines(session_path), sep = "\n")
  cat("\n```\n")
} else {
  cat("*Session info not yet generated.*\n")
}
```
